---
title: "Taxon-set enrichment analysis with TaxSEA"
teaching: 20
exercises: 0
---

:::::::::::::::::::::::::::::::::::::: questions 

- What is taxon-set enrichment analysis?
- How do we get started with the TaxSEA package?

::::::::::::::::::::::::::::::::::::::::::::::::

::::::::::::::::::::::::::::::::::::: objectives

- Placeholder
- Placeholder

::::::::::::::::::::::::::::::::::::::::::::::::

## Loading the package

You can also include figures generated from R Markdown:

```{r, echo=TRUE}

# Testing if package install.
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install("TaxSEA", version = "devel")

library(TaxSEA)

2+2

```

::::::::::::::::::::::::::::::::::::: callout

Callout sections can highlight information.

They are sometimes used to emphasise particularly important points
but are also used in some lessons to present "asides": 
content that is not central to the narrative of the lesson,
e.g. by providing the answer to a commonly-asked question.

::::::::::::::::::::::::::::::::::::::::::::::::

## Figures

You can also include figures generated from R Markdown:

```{r pyramid, fig.alt = "pie chart illusion of a pyramid", fig.cap = "Sun arise each and every morning"}
pie(
  c(Sky = 78, "Sunny side of pyramid" = 17, "Shady side of pyramid" = 5), 
  init.angle = 315, 
  col = c("deepskyblue", "yellow", "yellow3"), 
  border = FALSE
)
```



## Math

One of our episodes contains $\LaTeX$ equations when describing how to create
dynamic reports with {knitr}, so we now use mathjax to describe this:

`$\alpha = \dfrac{1}{(1 - \beta)^2}$` becomes: $\alpha = \dfrac{1}{(1 - \beta)^2}$

Cool, right?

::::::::::::::::::::::::::::::::::::: keypoints 

- Use `.md` files for episodes when you want static content
- Use `.Rmd` files for episodes when you need to generate output
- Run `sandpaper::check_lesson()` to identify any issues with your lesson
- Run `sandpaper::build_lesson()` to preview your lesson locally

::::::::::::::::::::::::::::::::::::::::::::::::

[r-markdown]: https://rmarkdown.rstudio.com/
